Semi-supervised author disambiguation of scientific publications

### 2015-07-16 paper.tex
autosave

Efforts and solutions to author disambiguation have been proposed from various
communities. On the one hand, libraries have maintained and developed
authorship control with manual curation

@@

% References ==================================================================
\nocite{langley00} % todo remove

>>>>

Efforts and solutions to author disambiguation have been proposed from various
communities \citep{liu2014author}. On the one hand, libraries have maintained
authorship control through manual curation, either in a centralized way by
hiring collaborators or by developing services inviting authors to register
their publications themselves (e.g., Google Scholar, Inspire-HEP). Recently,
efforts started to assign persistent digital identifiers to researchers (e.g.,
ORCID, ResearchedID), with the further objective to embed these identifiers in
the submission workflow of publishers or repositeries (e.g., Elsevier, arXiv,
Inspire-HEP), thereby univocally solving any disambiguation issue. With the
large cost of centralized manual authorship control or until the larger
adoption of crowdsourced solutions, the impact of these efforts are
unfortunately limited by the efficiency, motivation and integrity of their
active contributors. For these reasons, fully automated machine learning-based
methods have been proposed during the past decade to provide less costly and
more efficient solutions to author disambiguation. In this work, ...

@@

% References ==================================================================
